---
title: "ESF001s"
author: "Janica Bühler"
date: "4 Juni 2021"
output: html_document
---
```{r setup, include=FALSE}
library(plyr)
library(dplyr)
#library(stacy.hadcm.tools)
library(PaleoSpec)
library(nest)
library(tidyverse)
source("Functions/event_synchronization_2.R")
```

From Rehfeld&Kurths2014 Similarity estimators for irregular and age-uncertain time series we have a definition for event synchronization. 

Extreme event are all the events that are above or below the q/2 (1-q/2) percentiles of a distribution. The value of the event is now unimportant. Only time t\*_x (t\*_y) is considered.

Temporal threshold \tau defines within what timespan an event is connsidered as synchronous. 
\tau = max(\delta t^x, min(\delta t\*_x, \delta t\*_y)/2)
\delta t^x is the mean sampling rate of X, 
\delta t\*_x are the interevent times in X or Y

The co-occurence of an event in X and Y is counted and summed as C(X|Y) = \sum \sum J^{xy}_{lm},
where the counter variable J = 1 (if 0<t\*_x-t\*_y<\tau), = 1/2 if t\*_x-t\*_y = 0, and = 0 otherwise

The strength Q = (C(X|Y)+C(Y|X))/\sqrt(N_x*N_y), where N_i is the number of events in each TS
The direction q = (C(X|Y)-C(Y|X))/\sqrt(N_x*N_y)

```{r}
ENTITY_INFO <- read.csv("Data/SISAL1k_entity_info.csv")
FULL <- list(HadCM3 = list(), ECHAM5 = list(), GISS = list(), CESM = list(), isoGSM = list())
DOWN <- list(HadCM3 = list(), ECHAM5 = list(), GISS = list(), CESM = list(), isoGSM = list())
for(Model in c("HadCM3", "ECHAM5", "GISS", "CESM", "isoGSM")){
  FULL[[Model]] = read.csv(paste0("Data/SISAL1k_annual_",Model,".csv"))
  DOWN[[Model]] = read.csv(paste0("Data/SISAL1k_ds_", Model,".csv"))
}
rm(Model)

load("Data/Timeseries.RData")
```



SOLAR forcing:
```{r}
load("Data/Timeseries.RData")

#volc forcing:
solar_forcing <- Timeseries$solar

DATA_sol = list()
DATA_sol$time <- seq(1100,101,-1)
DATA_sol$value_SHB <- as.numeric(solar_forcing)[1:1000]
ECHAM5_solar = as.data.frame(read.delim("Data/ECHAM5_TSI_v2.txt")) %>% dplyr::rename("month" = "X1","year" = "X1.1" ,"sol" = "X1366.9914", "unc" ="X0.2")
ECHAM5_solar = ECHAM5_solar %>% filter(year>=850 & year < 1850)
DATA_sol$value_MSL <- zoo::rollapply(as.numeric(ECHAM5_solar$sol),12,mean, by = 12, na.rm = T)

Vieira_solar = read.delim("Data/tsi_VSK.txt", header = TRUE, sep = " ")
DATA_sol$value_VRA <- as.numeric(Vieira_solar$Vieira_Solanki_Krivova)

rm(solar_forcing)
```



```{r}
SYNCHRO <- list(
  speleo_oc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  speleo_o_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  speleo_c_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  sim_o_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  sim_o_volc_full = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  entity_list = list()
)

for(Model in c("HadCM3", "ECHAM5", "GISS", "isoGSM", "CESM")){
    if(Model %in% c("HadCM3", "GISS")){
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_SHB
    }else if(Model == "ECHAM5"){
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_MSL
    }else{
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_VRA
    }
  for(entity in ENTITY_INFO$entity_id){
    data_rec = DOWN[[Model]] %>% filter(entity_id == entity)
    data_full = FULL[[Model]] %>% filter(entity_id == entity)
    if(all(is.na(data_rec$d13C_measurement))){next}
  
    SYNCHRO$entity_list = c(SYNCHRO$entity_list, entity)
    #speleo_oc
    SYNCHRO$speleo_oc[[Model]][[paste0("ENTITY",entity)]] <- list(times = list(), tau = list())
    tmp = synchro_time(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec$d18O_measurement)], value = na.omit(data_rec$d18O_measurement))),
                       TS_2 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec$d13C_measurement)], value = na.omit(data_rec$d13C_measurement))), q = 5)
    SYNCHRO$speleo_oc[[Model]][[paste0("ENTITY",entity)]]$times = tmp$list_time
    SYNCHRO$speleo_oc[[Model]][[paste0("ENTITY",entity)]]$tau = tmp$tau
    
    for(isotope in c("o", "c")){
      if(isotope == "o"){
        value_here = data_rec$d18O_measurement
      }else{
        value_here = data_rec$d13C_measurement
      }
      
      #volc
      SYNCHRO[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]] <- list(times = list(), tau = list())
      tmp = synchro_time(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(value_here)], value = na.omit(value_here))),
                         TS_2 = irr_detrend(list(time = data_sol$time, value = data_sol$value)),volc = F, q = 5)
      SYNCHRO[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]]$times = tmp$list_time
      SYNCHRO[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]]$tau = tmp$tau
    }
    
    #model and volcano
    #for(modeled_var in c("o","p","t")){
    for(modeled_var in c("o")){
      if(modeled_var == "o"){var_name = "ITPC"}
      if(modeled_var == "p"){var_name = "PREC"}
      if(modeled_var == "t"){var_name = "TEMP"}
      
      #volc
      SYNCHRO[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]] <- list(times = list(), tau = list())
      tmp = synchro_time(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec[[var_name]])], value = na.omit(data_rec[[var_name]]))),
                         TS_2 = list(time = data_sol$time, value = data_sol$value),volc = F, q = 5)
      SYNCHRO[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]]$times = tmp$list_time
      SYNCHRO[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]]$tau = tmp$tau
      
      #volc full
      SYNCHRO[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]] <- list(times = list(), tau = list())
      tmp = synchro_time(TS_1 = irr_detrend(list(time = data_full$year_BP[!is.na(data_full[[var_name]])], value = na.omit(data_full[[var_name]]))),
                         TS_2 = list(time = data_sol$time, value = data_sol$value),volc = F, q = 5)
      SYNCHRO[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]]$times = tmp$list_time
      SYNCHRO[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]]$tau = tmp$tau
     
      
    }
  }
}

rm(entity, data_rec, isotope, modeled_var)

```

This repeats the first step but with permutating values (the time stays the same).

```{r}
SYNCHRO_SIG <- list(
  speleo_oc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  speleo_o_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  speleo_c_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  sim_o_volc = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  sim_o_volc_full = c(HadCM3 = list(), ECHAM5 = list(), GISS = list(), isoGSM = list(), CESM = list()),
  entity_list = list()
)

for(MC_repeat in 1:2000){
  if(MC_repeat%%10 == 1){print(MC_repeat)}
  for(Model in c("HadCM3", "ECHAM5", "GISS", "isoGSM", "CESM")){
    if(Model %in% c("HadCM3", "GISS")){
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_SHB
    }else if(Model == "ECHAM5"){
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_MSL
    }else{
      data_sol <- list()
      data_sol$time = DATA_sol$time
      data_sol$value = DATA_sol$value_VRA
    }
    for(entity in ENTITY_INFO$entity_id){
      data_rec = DOWN[[Model]] %>% filter(entity_id == entity)
      data_full = FULL[[Model]] %>% filter(entity_id == entity)
      if(all(is.na(data_rec$d13C_measurement))){next}
    
      SYNCHRO_SIG$entity_list = c(SYNCHRO_SIG$entity_list, entity)
      #speleo_oc
      SYNCHRO_SIG$speleo_oc[[Model]][[paste0("ENTITY",entity)]][[MC_repeat]] <- list(times = list(), tau = list())
      tmp = synchro_time_random.cut(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec$d18O_measurement)], value = na.omit(data_rec$d18O_measurement))),
                         TS_2 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec$d13C_measurement)], value = na.omit(data_rec$d13C_measurement))), q = 5)
      SYNCHRO_SIG$speleo_oc[[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$times = tmp$list_time
      SYNCHRO_SIG$speleo_oc[[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$tau = tmp$tau
      
      for(isotope in c("o", "c")){
        if(isotope == "o"){
          value_here = data_rec$d18O_measurement
        }else{
          value_here = data_rec$d13C_measurement
        }
        
        #volc
        SYNCHRO_SIG[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]] <- list(times = list(), tau = list())
        tmp = synchro_time_random.cut(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(value_here)], value = na.omit(value_here))),
                           TS_2 = irr_detrend(list(time = data_sol$time, value = data_sol$value)),volc = F, q = 5)
        SYNCHRO_SIG[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$times = tmp$list_time
        SYNCHRO_SIG[[paste0("speleo_",isotope,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$tau = tmp$tau
      }
      
      #model and volcano
      #for(modeled_var in c("o","p","t")){
      for(modeled_var in c("o")){
        if(modeled_var == "o"){var_name = "ITPC"}
        if(modeled_var == "p"){var_name = "PREC"}
        if(modeled_var == "t"){var_name = "TEMP"}
        
        #volc
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]] <- list(times = list(), tau = list())
        tmp = synchro_time_random.cut(TS_1 = irr_detrend(list(time = data_rec$year_BP[!is.na(data_rec[[var_name]])], value = na.omit(data_rec[[var_name]]))),
                           TS_2 = list(time = data_sol$time, value = data_sol$value),volc = F, q = 5)
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$times = tmp$list_time
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$tau = tmp$tau
        
        #volc full
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]] <- list(times = list(), tau = list())
        tmp = synchro_time_random.cut(TS_1 = irr_detrend(list(time = data_full$year_BP[!is.na(data_full[[var_name]])], value = na.omit(data_full[[var_name]]))),
                           TS_2 = list(time = data_sol$time, value = data_sol$value),volc = F, q = 5)
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$times = tmp$list_time
        SYNCHRO_SIG[[paste0("sim_",modeled_var,"_volc_full")]][[Model]][[paste0("ENTITY",entity)]][[MC_repeat]]$tau = tmp$tau
       
        
      }
    }
  }
}

rm(entity, data_rec, isotope, modeled_var)

#save(SYNCHRO_SIG, file = "SYNCHRO_SIG_2000_solar.RData")

```

# Tau -> Bin Size
Calculate mean tau so we can determine the bin size that makes the most sense. 
```{r}
tau = c()
for(Model in c("HadCM3", "ECHAM5", "GISS", "isoGSM", "CESM")){
  for(entity in ENTITY_INFO$entity_id){
    data_rec = DOWN[[Model]] %>% filter(entity_id == entity)
    if(all(is.na(data_rec$d13C_measurement))){next}
    tau = c(tau, mean(SYNCHRO$speleo_oc[[Model]][[paste0("ENTITY", entity)]]$tau))
  }
}

hist(as.numeric(tau))
abline(v=median(as.numeric(tau), na.rm = T), col = "red")
mtext(at= (median(as.numeric(tau), na.rm = T)+6), line = -3, text = round(median(as.numeric(tau), na.rm = T), digits = 3), col = "red")

bstrap <- c()
for (i in 1:1000){
  bstrap <- c(bstrap,median(sample(tau,length(tau),replace=T), na.rm = T))
}

print(paste0("Median tau : ", round(median(tau, na.rm = T),digits = 2), "[‰^2],",
                 " 90% CI: (", round(quantile(bstrap,0.05), digits = 2), ", ", round(quantile(bstrap,0.95), digits = 2), ")"))


```

# Histogram bins
Calculate histogram bins
This also includes the bins for the determination of the significance. If the "real" count is higher than the 95% quantile of the permutated count, then the column will be plotted as non-transparent. 
```{r}
bin_size = 10
bin_borders = seq(1100, 100, by = -bin_size)
hist_real = list()
hist_sig  = list()
hist_sig_95  = list()

for(option in c("speleo_oc", "speleo_o_volc", "speleo_c_volc", "sim_o_volc", "sim_o_volc_full")){
  
  hist_real[[option]] = numeric(length(bin_borders)-1)
  hist_sig[[option]] = matrix(numeric((length(bin_borders)-1)*MC_repeat), ncol = MC_repeat)
  hist_sig_95[[option]] = numeric(length(bin_borders)-1)
  
  for(time_pos in 1:(length(bin_borders)-1)){
    for(Model in c("HadCM3", "ECHAM5", "GISS", "isoGSM", "CESM")){
      for(entity in 1:length(SYNCHRO[[option]][[Model]])){
        times_real = SYNCHRO[[option]][[Model]][[entity]]$times
        if(sum(times_real>bin_borders[time_pos]&times_real<=bin_borders[time_pos-1])>0){hist_real[[option]][time_pos] = hist_real[[option]][time_pos]+1}
        for(rep in 1:MC_repeat){
          times_sig = SYNCHRO_SIG[[option]][[Model]][[entity]][[rep]]$times
          if(is_empty(times_sig)){next}
          if(sum(times_sig>bin_borders[time_pos+1]&times_sig<=bin_borders[time_pos])>0){hist_sig[[option]][time_pos,rep] = hist_sig[[option]][time_pos,rep]+1}
        }
      }
    }
  }
  hist_sig_95[[option]] = apply(hist_sig[[option]], 1, quantile, probs = 0.95, na.rm = T)
}

```


```{r}
hist_plot = hist_real$speleo_oc
hist_trans = hist_real$speleo_oc

hist_plot[hist_plot<hist_sig_95$speleo_oc] = NA
hist_trans[!hist_plot<hist_sig_95$speleo_oc] = NA

plot(0, ylim=c(0,10*5), xlim = c(800,1900), 
     main = "", xlab = "", ylab = "", axes = F)
axis(1,      col="black",at=c(800,1000,1200,1400,1600,1800),labels=FALSE)
mtext(side=1,col="black",at=c(800,1000,1200,1400,1600,1800),c(800,1000,1200,1400,1600,1800),line=1,las=1,cex=1)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = "red", type = "h", lw = 3)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor("red", alpha.f = 0.5), type = "h")
#barplot(hist_plot, col = "red", border = NA, add = T)
#barplot(hist_trans, col = adjustcolor("black", alpha = 0.5), add = T, border = NA)


```



Plotting:
```{r message=FALSE, warning=FALSE}

xlimz = c(800,1900)
col_volc <- "gray50"
axisnumscex <- 0.75
axslinno <- 1.1 #0.75
unitscex <- 1.1 #0.75
unitslinno <- 5 #2.5
namlin <- 1 #0.5
namcex <- 1 #1
cex_text <- 1.3
lwidth = 1.5


cols = c("#B2182B", "#b2182b", "#2166ac", "grey20", RColorBrewer::brewer.pal(9, "PRGn")[2], RColorBrewer::brewer.pal(9, "PRGn")[8])
ylimz = c(0,55)

box_color = "grey90"

pdf(file = paste0("Plots/Supplements/Manuscript_6_ESF_solar.pdf"), width = 8, height = 5)
par(mfrow = c(2,2), oma = c(0,1,0.5,0), mar = c(2, 2.5, 0, 0.5) + 0.1)

#a) Speleo co
hist_plot = hist_real$speleo_oc/2.9
hist_trans = hist_real$speleo_oc/2.9

hist_plot[hist_plot<hist_sig_95$speleo_oc/2.9] = NA
hist_trans[!hist_plot<hist_sig_95$speleo_oc/2.9] = NA
hist_plot[hist_plot == 0] = NA
hist_trans[hist_trans == 0] = NA


plot(0, ylim=ylimz, xlim = xlimz, 
     main = "", xlab = "", ylab = "", axes = F)
#rect(1050, par('usr')[3], 1150, par('usr')[4], col = box_color, border = NA)
#rect(1240, par('usr')[3], 1280, par('usr')[4], col = box_color, border = NA)
#rect(1430, par('usr')[3], 1470, par('usr')[4], col = box_color, border = NA)
#rect(1795, par('usr')[3], 1835, par('usr')[4], col = box_color, border = NA)
grid (NULL,NULL, lty = 6, col = "grey50") 
axis(1,      col="black",at=c(800,1000,1200,1400,1600,1800),labels=FALSE)
mtext(side=1,col="black",at=c(800,1000,1200,1400,1600,1800),c(800,1000,1200,1400,1600,1800),line=1,las=1,cex=axisnumscex)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = adjustcolor(cols[1], alpha.f = 0.9), type = "h", lw = lwidth)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor(cols[1], alpha.f = 0.2), type = "h", lw = lwidth)

mtext(expression(paste(plain("speleo-"),delta^{plain(18)}, plain("O-"),delta^{plain(13)}, plain(C))), side = 3, line = -1.5, adj = 0.95, col = cols[1])
#mtext(expression(paste(plain("volcano and speleo-"),delta^{plain(18)}, plain("O"))), side = 3, line = -2.5, adj = 0.95, col = adjustcolor(cols[4], alpha.f = 0.9))
mtext("   a)", side = 3, line = -1.5, adj = 0, col = "black")

axis(2,col="black",      at=c(0,10,20,30,40,50),labels=FALSE)
mtext(side=2,col="black",at=c(0,10,20,30,40,50),c("0%","10%","20%","30%","40%", "50%"),line=axslinno,las=1,cex=axisnumscex)

box(col = "black")


#b) Volc to Speleo o and speleo c
hist_plot = hist_real$speleo_o_volc/2.9
hist_trans = hist_real$speleo_o_volc/2.9

hist_plot[hist_plot<hist_sig_95$speleo_o_volc/2.9] = NA
hist_trans[!hist_plot<hist_sig_95$speleo_o_volc/2.9] = NA
hist_plot[hist_plot == 0] = NA
hist_trans[hist_trans == 0] = NA

plot(0, ylim=ylimz, xlim = xlimz, 
     main = "", xlab = "", ylab = "", axes = F)
#rect(1050, par('usr')[3], 1150, par('usr')[4], col = box_color, border = NA)
rect(1240, par('usr')[3], 1280, par('usr')[4], col = box_color, border = NA)
rect(1430, par('usr')[3], 1470, par('usr')[4], col = box_color, border = NA)
rect(1795, par('usr')[3], 1835, par('usr')[4], col = box_color, border = NA)
grid (NULL,NULL, lty = 6, col = "grey50") 
axis(1,      col="black",at=c(800,1000,1200,1400,1600,1800),labels=FALSE)
mtext(side=1,col="black",at=c(800,1000,1200,1400,1600,1800),c(800,1000,1200,1400,1600,1800),line=1,las=1,cex=axisnumscex)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = adjustcolor(cols[5], alpha.f = 0.9), type = "h", lw = lwidth)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor(cols[5], alpha.f = 0.2), type = "h", lw = lwidth)

hist_plot = hist_real$speleo_c_volc/2.9
hist_trans = hist_real$speleo_c_volc/2.9

hist_plot[hist_plot<hist_sig_95$speleo_c_volc/2.9] = NA
hist_trans[!hist_plot<hist_sig_95$speleo_c_volc/2.9] = NA
hist_plot[hist_plot == 0] = NA
hist_trans[hist_trans == 0] = NA

lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = adjustcolor(cols[6], alpha.f = 0.9), type = "h", lw = lwidth)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor(cols[6], alpha.f = 0.2), type = "h", lw = lwidth)

#mtext(expression(paste(plain("speleo-"),delta^{plain(18)}, plain("O-"),delta^{plain(13)}, plain(C))), side = 3, line = -1.5, adj = 0.95, col = cols[1])
mtext(expression(paste(plain("solar and speleo-"),delta^{plain(18)}, plain("O"))), side = 3, line = -1.5, adj = 0.95, col = adjustcolor(cols[5], alpha.f = 0.9))
mtext(expression(paste(plain("solar and speleo-"),delta^{plain(13)}, plain("C"))), side = 3, line = -2.5, adj = 0.95, col = adjustcolor(cols[6], alpha.f = 0.9))
mtext("   b)", side = 3, line = -1.5, adj = 0, col = "black")

axis(2,col="black",      at=c(0,10,20,30,40,50),labels=FALSE)
mtext(side=2,col="black",at=c(0,10,20,30,40,50),c("0%","10%","20%","30%","40%", "50%"),line=axslinno,las=1,cex=axisnumscex)

box(col = "black")

#c) downsampled simulation and volcano

hist_plot = hist_real$sim_o_volc/2.9
hist_trans = hist_real$sim_o_volc/2.9

hist_plot[hist_plot<hist_sig_95$sim_o_volc/2.9] = NA
hist_trans[!hist_plot<hist_sig_95$sim_o_volc/2.9] = NA
hist_plot[hist_plot == 0] = NA
hist_trans[hist_trans == 0] = NA

plot(0, ylim=ylimz, xlim = xlimz, 
     main = "", xlab = "", ylab = "", axes = F)
#rect(1050, par('usr')[3], 1150, par('usr')[4], col = box_color, border = NA)
rect(1240, par('usr')[3], 1280, par('usr')[4], col = box_color, border = NA)
rect(1430, par('usr')[3], 1470, par('usr')[4], col = box_color, border = NA)
rect(1795, par('usr')[3], 1835, par('usr')[4], col = box_color, border = NA)
grid (NULL,NULL, lty = 6, col = "grey50") 
axis(1,      col="black",at=c(800,1000,1200,1400,1600,1800),labels=FALSE)
mtext(side=1,col="black",at=c(800,1000,1200,1400,1600,1800),c(800,1000,1200,1400,1600,1800),line=1,las=1,cex=axisnumscex)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = adjustcolor(cols[3], alpha.f = 0.9), type = "h", lw = lwidth)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor(cols[3], alpha.f = 0.2), type = "h", lw = lwidth)

mtext(expression(paste(plain("solar and sim-"),delta^{plain(18)}, plain("O (ds)"))), side = 3, line = -1.5, adj = 0.95, col = cols[3])
mtext("   c)", side = 3, line = -1.5, adj = 0, col = "black")

axis(2,col="black",      at=c(0,10,20,30,40,50),labels=FALSE)
mtext(side=2,col="black",at=c(0,10,20,30,40,50),c("0%","10%","20%","30%","40%", "50%"),line=axslinno,las=1,cex=axisnumscex)

box(col = "black")

#d) annual simulation and volcano

hist_plot = hist_real$sim_o_volc_full/2.9
hist_trans = hist_real$sim_o_volc_full/2.9

hist_plot[hist_plot<hist_sig_95$sim_o_volc_full/2.9] = NA
hist_trans[!hist_plot<hist_sig_95$sim_o_volc_full/2.9] = NA
hist_plot[hist_plot == 0] = NA
hist_trans[hist_trans == 0] = NA

plot(0, ylim=ylimz, xlim = xlimz, 
     main = "", xlab = "", ylab = "", axes = F)
#rect(1050, par('usr')[3], 1150, par('usr')[4], col = box_color, border = NA)
rect(1240, par('usr')[3], 1280, par('usr')[4], col = box_color, border = NA)
rect(1430, par('usr')[3], 1470, par('usr')[4], col = box_color, border = NA)
rect(1795, par('usr')[3], 1835, par('usr')[4], col = box_color, border = NA)
grid (NULL,NULL, lty = 6, col = "grey50") 
axis(1,      col="black",at=c(800,1000,1200,1400,1600,1800),labels=FALSE)
mtext(side=1,col="black",at=c(800,1000,1200,1400,1600,1800),c(800,1000,1200,1400,1600,1800),line=1,las=1,cex=axisnumscex)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_plot, col = adjustcolor(cols[3], alpha.f = 0.9), type = "h", lw = lwidth)
lines(1950-(bin_borders[1:(length(bin_borders)-1)]-0.5), hist_trans, col = adjustcolor(cols[3], alpha.f = 0.2), type = "h", lw = lwidth)

mtext(expression(paste(plain("solar and sim-"),delta^{plain(18)}, plain("O (annual)"))), side = 3, line = -1.5, adj = 0.95, col = cols[3])
mtext("   d)", side = 3, line = -1.5, adj = 0, col = "black")

axis(2,col="black",      at=c(0,10,20,30,40,50),labels=FALSE)
mtext(side=2,col="black",at=c(0,10,20,30,40,50),c("0%","10%","20%","30%","40%", "50%"),line=axslinno,las=1,cex=axisnumscex)

box(col = "black")


rm(axisnumscex, axslinno, cex_text, col_solar, col_volc, cols, hmax, namcex, namlin, nr_breaks, unitscex,unitslinno, xlimz, Timeseries, hist_plot, hist_trans)

dev.off()

```
